Disparity through time - for appendix

### 2017-12-15 analyses/10-appendix-dtt-figures.Rmd
Add legend

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5)) +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

@@

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5)) +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

>>>>

# Modify data - add midpoints, remove missing data, 
# make disparity relative by dividing by max values
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank())

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none") +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none")

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.key.size = unit(0.2, "in"),
        legend.text = element_text(size = 8),
        legend.title=element_blank())

@@

# Modify data - add midpoints, remove missing data
strat2 <- 
  strat %>%
  mutate(time = unlist(z)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(relative.disparity = bs.median/max(bs.median)) %>%
  mutate(relative.lwr = `2.5%`/max(bs.median)) %>%
  mutate(relative.upr = `97.5%`/max(bs.median))

@@

beck_base <- 
  ggplot(strat2, aes(y = relative.disparity, x = time, colour = model)) +
  theme_classic(base_size = 12) + 
  scale_y_continuous(breaks = seq(0, 1, 0.5), 
                     labels = seq(0, 1, 0.5)) +
  scale_x_reverse(limits = c(100, 0),
                  breaks = c(seq(100, 0, by = -50))) +
  expand_limits(x = 0, y = c(0,1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        )

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none") +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.position = "none")

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5),
        legend.key.size = unit(0.2, "in"),
        legend.text = element_text(size = 8),
        legend.title=element_blank())
